MSHS COVID-19 Vaccine Schedule Tracking

### 2021-10-27 Amb_Sched_Tracking.Rmd
Add logic to account for future appointments erroneously marked as arrived.

```{r Format and preprocess raw schedule data}
sched_data <- raw_data %>%
  filter(Patient != "Patient, Test") %>%
  rename(MadeDate = `Made Date`,
         IsPtEmployee = `Is the patient a Mount Sinai employee`) %>%
  mutate(DOB = as.Date(DOB, format = "%m/%d/%Y"),
         MadeDate = as.Date(MadeDate, format = "%m/%d/%y"),
         ApptDate = as.Date(Date, format = "%m/%d/%Y"),
         # Clean up department if it is duplicated in that column
         Department = ifelse(str_detect(Department, ","),
                        substr(Department, 1,
                               str_locate(Department, ",") - 1),
                        Department),
         # Group arrived, completed, and checked out appointments as arrived
         Status = ifelse(`Appt Status` %in% c("Arrived", "Comp", "Checked Out"),
                         "Arr", `Appt Status`),
         # Update appointment status: classify any appts from prior days that are
         # still in scheduled as No Shows
         Status2 = ifelse(ApptDate < (today) & Status == "Sch", "No Show", 
                          # Correct any appts erroneously marked as arrived early
                          ifelse(report_date < today &
                                   ApptDate >= today &
                                   Status == "Arr", "Sch",
                                 Status)),
         # Determine whether appointment is for dose 1, 2, or 3 based on
         # scheduled visit type
         Dose = ifelse(str_detect(Type, "DOSE 1"), 1,
                       ifelse(str_detect(Type, "DOSE 2"), 2,
                              ifelse(str_detect(Type, "DOSE 3"), 3, NA))))

>>>>

```{r Format and preprocess raw schedule data}
sched_data <- raw_data %>%
  filter(Patient != "Patient, Test") %>%
  rename(MadeDate = `Made Date`,
         IsPtEmployee = `Is the patient a Mount Sinai employee`) %>%
  mutate(DOB = as.Date(DOB, format = "%m/%d/%Y"),
         MadeDate = as.Date(MadeDate, format = "%m/%d/%y"),
         ApptDate = as.Date(Date, format = "%m/%d/%Y"),
         # Clean up department if it is duplicated in that column
         Department = ifelse(str_detect(Department, ","),
                        substr(Department, 1,
                               str_locate(Department, ",") - 1),
                        Department),
         # Group arrived, completed, and checked out appointments as arrived
         Status = ifelse(`Appt Status` %in% c("Arrived", "Comp", "Checked Out"),
                         "Arr", `Appt Status`),
         # Update appointment status: classify any appts from prior days that are
         # still in scheduled as No Shows
         Status2 = ifelse(ApptDate < (today) & Status == "Sch", "No Show", 
                          # Correct any appts erroneously marked as arrived early
                          ifelse((report_date < today &
                                    ApptDate >= today &
                                    Status == "Arr") |
                                   (ApptDate > today & Status == "Arr"), "Sch",
                                 Status)),
         # Determine whether appointment is for dose 1, 2, or 3 based on
         # scheduled visit type
         Dose = ifelse(str_detect(Type, "DOSE 1"), 1,
                       ifelse(str_detect(Type, "DOSE 2"), 2,
                              ifelse(str_detect(Type, "DOSE 3"), 3, NA))))
